Imputation of incomplete multilevel data

### 2024-07-05 manuscript.qmd
fix singularity issue, but MI is still more biased than list-wise deletion

```{r}
dat$extraversion_experience <- NA
```

@@

### Analyze imputed data

@@

@@

#### Model with with cross-level interaction

@@

@@

>>>>

```{r}
dat$extraversion_experience <- dat$extraversion_ij * dat$experience_j
```

@@

## Analyze imputed data

@@

```{r}
mod_imp_randomslope <- with(
  imp,
  lmer(
    popularity_ij ~ gender_ij + extraversion_ij + experience_j + 
      (1  + extraversion_ij | cluster_id), 
    control = lmerControl(optCtrl = list(maxfun = 2e5)), REML = FALSE
    )
  )
```

Still no convergence. Use different mixed modeling technique.

```{r}
library(nlme)
mod_imp_randomslope <- with(
  imp,
  lme(
    popularity_ij ~ gender_ij + extraversion_ij + experience_j, 
    random = ~ 1  + extraversion_ij | cluster_id))
```

@@

Model with with cross-level interaction

@@

Does not converge. Use `nmle` again.
```{r}
mod_imp_interaction <- with(
  imp,
  lme(
    popularity_ij ~ gender_ij + extraversion_ij + experience_j +
      extraversion_ij:experience_j, 
    random = ~ 1  + extraversion_ij | cluster_id))
```

@@

## Compare estimates

```{r}
est_true <-
  mod_true_interaction |> tidy() |> select(term, true = estimate)
est_cca <- 
  mod_cca_interaction |> tidy() |> select(cca = estimate)
est_imp <- pool(mod_imp_interaction) |> tidy() |> select(imp = estimate)
cbind(est_true[1:5,], est_cca[1:5,], est_imp)
```

The estimates after imputation are more biased than the CCA estimates after list-wise deletion.
